---
title: "foraging-online-4"
output: 
  html_document:
    toc: true
    keep_md: TRUE
---
<style type="text/css">
.main-container {
  max-width: 1800px;
  margin-left: auto;
  margin-right: auto;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, comment=NA, warning=FALSE, message=F)
options(width = 220)
```

```{r libs, message=F}
if(!require(tidyverse)){install.packages("tidyverse")}
if(!require(ggpubr)){install.packages("ggpubr")} # for correlation geom, see  https://rpkgs.datanovia.com/ggpubr/reference/stat_cor.html
```

```{r}
d = read_csv(
  "d3_trial_by_trial.csv",
  col_types=cols(
    condition=col_factor(), subject=col_factor(), trial=col_factor(), 
    score=col_integer(), ignap=col_double(), ignba=col_double(), icint=col_double()
    )
  )
```

"Rejection rate" is the rejection rate for apples. In the 40-banana 40-apple condition, the best strategy is to ignore apples to concentrate on bananas that are relatively plentiful, rejection rate should be high. In the 10-banana 70-apple condition, the best strategy is to eat all the fruit you come across, so rejection rates should be lower.

```{r}
ggplot(d, aes(y=ignap,x=condition)) +
  geom_boxplot()
```



